### 2016-12-07 Paper_v1.tex
Dec7_2

Gene knockouts in the electron transport chain significantly reduced the performance of the CFPS reaction (Fig.~\ref{fig:oxphos_ko}).
A key finding of both the CAT and overall system state sensitivity analysis was the importance of oxidative phosphorylation.
To investigate this further, we knocked out key oxidative phosphorylation reactions in the ensemble of kinetic models to examine the effect on glucose uptake and CAT production.
%A single \textit{cyd} knockout reduced the CAT carbon yield from 7.9\% to 2.6\% (Table~\ref{tbl:yield_breakdown}).
A single \textit{cyd} knockout reduced the CAT carbon yield from 2.7\% to 0.9\% (Table~\ref{tbl:yield_breakdown}).
In addition, the glucose uptake rate was reduced compared to that of the control (no knockouts).
%On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
%reducing the CAT carbon yield to 6.9\%; however, the glucose uptake rate remained similar to that of the control.
On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
reducing the CAT carbon yield to 2.3\%; however, the glucose uptake rate remained similar to that of the control.
%Knocking out \textit{app} increased CAT yield to 8.3\%, but this increase was not statistically significantly different from that of the control.
Knocking out \textit{app} did not change the CAT yield (it remained at 2.7\%).
%Lastly, knocking out all three reactions reduced the CAT yield to 3.0\%, but this was not statistically significantly different from the \textit{cyd} knockout alone.
Lastly, knocking out all three reactions reduced the CAT yield to 0.7\%, similar to knocking out the \textit{cyd} alone.
Thus, the model suggested the key step in oxidative phosphorylation was catalyzed by the gene product of \textit{cyd}.
However, while disruption of \textit{cyd} significantly reduced the CAT carbon yield, it did not eliminate the ability of CFPS reaction to produce CAT.
This suggested there was a mixture of energy sources supporting CAT production, with the most significant being oxidative phosphorylation.
%The \textit{cyd} enzyme is responsible for transferring electrons with oxygen as an electron acceptor allowing the release of energy to form ATP.
%The sensitivity analysis showed oxidative phosphorylation was significant for CAT production as well as the system state.
A similar distribution of the carbon contribution to CAT yield was seen across the best-fit set and all knockouts.
In all cases, glutamate was responsible for about two-thirds of carbon consumption toward CAT.
This was due to its role in generating other amino acids and as a possible energy source for metabolism.
The much greater consumption of this one amino acid was made possible by its much larger initial condition, as it was present in the cell media in the form of magnesium glutamate, ammonium glutamate, and potassium glutamate [CITE? THESIS NOT CURRENTLY IN BIBLIOGRAPHY].
Glucose made the next largest contribution, between 20\% and 30\%, dwarfing all amino acids other than glutamate.
This makes sense, as glucose powers the entire metabolism during the first hour, including energy species synthesis and amino acid synthesis.
The knockouts in oxidative phosphorylation also reduced the energy efficiency of CAT production  (Fig.~\ref{fig:oxphos_ko}).
The best-fit set, $\Delta$app, and experimental dataset had efficiencies of 2.6\%, $\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
This was in line with the effect of knockouts on yield, which in turn was more or less proportional to the total amount of CAT produced in each case.
Taken together, these results show that oxidative phosphorylation, particularly \textit{cyd}, is important to efficient CAT production.

Furthermore, we examined the proportion of amino acid consumption that was due to CAT synthesis in the best-fit set (Table~\ref{tbl:AA_breakdown}).
Eight of the 20 amino acids had a percentage of 100\% or higher.
For six of these (isoleucine, leucine, methionine, phenylalanine, tryptophan, valine), synthesis was inactive or negligible, meaning that CAT synthesis was the only reaction that consumed these species.
This is why methionine, and to a lesser extent isoleucine, leucine, and valine do not fit the experimental data as well as some other amino acids; consumption via CAT synthesis was not enough to fit the data, and no other reactions exist in the network to consume these species.
For histidine and tyrosine, synthesis was active, allowing the percentage to be higher than 100\%.
Another ten amino acids registered percentages lower than 100\%, meaning that they were consumed by other pathways in the network.
The most extreme of these is glutamate, with a percentage of 0.2\%, because it was consumed by numerous reactions for the synthesis of other amino acids and as an energy substrate.
Likewise, arginine, asparagine, glycine, and proline are consumed in the production of other amino acids, while cysteine and lysine are consumed to form other metabolites.
%ARG R_arg_deg1-4 go to GLU
%ASN R_asn_deg goes to ASP
%ASP R_thr, maybe negligible
%CYS cys_deg goes to pyr
%GLY R_gar goes to GLU
%LYS lys_deg goes to cadav
%PRO pro_deg goes to GLU
%SER R_glyA, maybe negligible
%THR R_thr_deg4, maybe negligible
Finally, alanine and glutamine increased during the timecourse, meaning that synthesis outweighed all consumption (including consumption toward CAT).

Sequence-specific flux balance analysis (ssFBA) predicted optimal CAT yields with no adjustable parameters (Fig.~\ref{fig:CATProdYield}).
Before exploring CFPS optimality, we first validated the ssFBA approach by comparing simulated and measured concentrations of CAT for the first hour of glucose consumption.
We chose this time window (during the first phase of CAT production) because it was approximately linear in both glucose consumption and by-/production formation.
The ssFBA calculation had no adjustable parameters; bounds on transcription and translation rates, and biochemical fluxes were either estimated from data, or
from mechanistic models parameterized from literature.
Uncertainty in experimental factors such as RNA polymerase, ribosome concentrations, elongation rates, or the upper bounds for oxygen and glucose consumption rates was addressed
by sampling plausible ranges for these parameters.
The ensemble of ssFBA simulations predicted CAT formation as a function of time during the first hour of production when constrained by the experimental metabolite data (Fig.~\ref{fig:CATProdYield}A).
Thus, the molecular description of transcription and translation were consistent with experimental measurements.
Next, to gauge the performance of the CFPS reaction, we next calculated the CAT carbon yield for three classes of constraints:
(i) theoretical maximum glucose, amino acid and oxygen upper bounds, and realistic transcriptional/translational constraints;
(ii) theoretical maximum glucose, amino acid and oxygen upper bounds, realistic transcriptional/translational constraints and knockouts of amino acid synthesis reactions of amino acids supplemented in the \textit{E. coli} extract preparation.  
(iii) metabolite fluxes constrained by the CAT data, and realistic transcriptional/translational constraints and knockouts of amino acid synthesis reactions of amino acids supplemented in the \textit{E. coli} extract preparation (Fig.~\ref{fig:CATProdYield}B).
The physiological theoretical maximum CAT carbon yield (case i) was 21.8\% $\pm$ 2.8\% (Fig.~\ref{fig:CATProdYield}B, left); this represents optimal network performance if glucose, oxygen and amino acids were produced or consumed at their upper bounds, with bounded transcription and translation rates (96\% without glucose contribution in the carbon yield calculation).
For case ii, the optimal CAT carbon yield decreased to 18.2\% $\pm$ 3.0\% (Fig.~\ref{fig:CATProdYield}B, middle).
Lastly, when metabolite constraints were applied with experimental measurements of measurements (case iii), the predicted carbon yield was 6.0\% $\pm$ 2.0\%
%By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield of 8.6\% $\pm$ 0.4\%, equivalent to 23\% of the theoretical maximum (i) and 35\% of the physiological case (ii).
By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield (without arginine and glutamate) of 7.9\%, equivalent to 36\% of the optimal case (i).
The experimental dataset had a CAT carbon yield of 8.2\%, similar to both the kinetic model and the experimentally constrained ssFBA calculation (case iii).
However, the energy efficiency for case i was 18.1\% and 15.5\% for the second case, while for the experimentally constrained case it was 3.9\%.  
Thus, while the CFPS reaction was not optimal, the ssFBA calculations suggested that an approximately three-fold increase in carbon yield was theoretically possible.

@@

\begin{table}
\centering
    \caption{CAT carbon yield breakdown for best-fit set, knockouts, and experimental data. Carbon produced as CAT, carbon consumed as glucose and each amino acid, sum of consumed species (with and without arginine and glutamate), and yield  (with and without arginine and glutamate). Energy efficiency for best-fit set, knockouts, and experimental data.}
    \renewcommand{\arraystretch}{1.25}
    \begin{tabular}{lrrrrrr} \toprule
        Carbon Produced (mM) & Best-fit & $\Delta$cyd & $\Delta$nuo & $\Delta$app & $\Delta$cyd $\Delta$nuo $\Delta$app & Data \\ \hline
        CAT & 20.9 & 6.5 & 18.1 & 21.4 & 5.1 & 21.6 \\ \midrule
        Carbon Consumed (mM) \\ \hline
        GLC & 215.4 & 215.4 & 215.4 & 215.4 & 159.8 & 215.4 \\ \hline
        ALA & 0.0 & 0.0 & 1.7 & 0.0 & 0.0 & 0.0 \\ \hline
        ARG & 10.2 & 0.9 & 1.1 & 9.9 & 1.3 & - \\ \hline
        ASN & 6.2 & 6.3 & 6.2 & 6.2 & 6.3 & 6.3 \\ \hline
        ASP & 7.5 & 0.0 & 3.9 & 7.5 & 0.0 & 9.6 \\ \hline
        CYS & 3.0 & 2.9 & 3.0 & 3.1 & 2.9 & 3.7 \\ \hline
        GLN & 0.0 & 1.8 & 0.0 & 0.0 & 2.7 & 0.0 \\ \hline
        GLU & 492.6 & 505.1 & 528.2 & 505.6 & 501.8 & - \\ \hline
        GLY & 3.1 & 1.1 & 2.6 & 3.1 & 0.9 & 1.5 \\ \hline
        HIS & 0.2 & 0.4 & 1.1 & 0.2 & 0.3 & 0.0 \\ \hline
        ILE & 1.0 & 0.3 & 0.8 & 1.0 & 0.2 & 1.7 \\ \hline
        LEU & 1.4 & 0.4 & 1.2 & 1.4 & 0.3 & 2 \\ \hline
        LYS & 10.7 & 13.2 & 13.1 & 10.7 & 13.2 & 8.3 \\ \hline
        MET & 0.8 & 0.2 & 0.7 & 0.8 & 0.2 & 2.9 \\ \hline
        PHE & 3.2 & 1.0 & 2.8 & 3.3 & 0.8 & 1.6 \\ \hline
        PRO & 2.4 & 0.2 & 0.7 & 2.4 & 0.2 & 1.9 \\ \hline
        SER & 2.5 & 2.1 & 2.4 & 2.5 & 2.1 & 1.8 \\ \hline
        THR & 3.4 & 2.9 & 3.3 & 3.4 & 2.8 & 2.8 \\ \hline
        TRP & 1.0 & 0.3 & 0.8 & 1.0 & 0.2 & 1.2 \\ \hline
        TYR & 1.1 & 0.4 & 1.1 & 1.1 & 0.4 & 0.6 \\ \hline
        VAL & 1.4 & 0.4 & 1.2 & 1.5 & 0.4 & 2.4 \\ \midrule
        Sum & 767.1 & 755.3 & 791.3 & 780.1 & 696.8 & - \\ \hline
        Sum w/o ARG,GLU & 264.3 & 249.3 & 262.0 & 264.6 & 193.7 & 263.7 \\ \midrule
        Yield & 2.7\% & 0.9\% & 2.3\% & 2.7\% & 0.7\% & - \\ \hline
        Yield w/o ARG, GLU & 7.9\% & 2.6\% & 6.9\% & 8.1\% & 2.7\% & 8.2\% \\ \midrule
%        Energy Efficiency & 1.8\% & 0.6\% & 1.6\% & 1.8\% & 0.6\% & 1.9\% \\ \bottomrule
        Energy Efficiency & 2.6\% & 0.8\% & 2.2\% & 2.6\% & 0.8\% & 2.6\% \\ \bottomrule
%        Efficiencies based on ATP number of 17: 2.558085 & 0.788758 & 2.210560 & 2.611583 & 0.847068 & 2.644330
(CAT[end]-CAT[1])*(2*219+438)/((glc[1]-glc[end])*17)*100

    \end{tabular}
\label{tbl:yield_breakdown}
\end{table}

>>>>

Gene knockouts in the electron transport chain significantly reduced the performance of the CFPS reaction (Fig.~\ref{fig:oxphos_ko}).
A key finding of both the CAT and overall system state sensitivity analysis was the importance of oxidative phosphorylation.
To investigate this further, we knocked out key oxidative phosphorylation reactions in the ensemble of kinetic models to examine the effect on glucose uptake and CAT production.
%A single \textit{cyd} knockout reduced the CAT carbon yield from 7.9\% to 2.6\% (Table~\ref{tbl:yield_breakdown}).
A single \textit{cyd} knockout reduced the CAT carbon yield from 2.7\% to 0.9\% (Table~\ref{tbl:yield_breakdown}).
In addition, the glucose uptake rate was reduced compared to that of the control (no knockouts).
%On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
%reducing the CAT carbon yield to 6.9\%; however, the glucose uptake rate remained similar to that of the control.
On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
reducing the CAT carbon yield to 2.3\%; however, the glucose uptake rate remained similar to that of the control.
%Knocking out \textit{app} increased CAT yield to 8.3\%, but this increase was not statistically significantly different from that of the control.
Knocking out \textit{app} did not change the CAT yield (it remained at 2.7\%).
%Lastly, knocking out all three reactions reduced the CAT yield to 3.0\%, but this was not statistically significantly different from the \textit{cyd} knockout alone.
Lastly, knocking out all three reactions reduced the CAT yield to 0.7\%, similar to knocking out the \textit{cyd} alone.
Thus, the model suggested the key step in oxidative phosphorylation was catalyzed by the gene product of \textit{cyd}.
However, while disruption of \textit{cyd} significantly reduced the CAT carbon yield, it did not eliminate the ability of CFPS reaction to produce CAT.
This suggested there was a mixture of energy sources supporting CAT production, with the most significant being oxidative phosphorylation.
%The \textit{cyd} enzyme is responsible for transferring electrons with oxygen as an electron acceptor allowing the release of energy to form ATP.
%The sensitivity analysis showed oxidative phosphorylation was significant for CAT production as well as the system state.
A similar distribution of the carbon contribution to CAT yield was seen across the best-fit set and all knockouts.
In all cases, glutamate was responsible for about two-thirds of carbon consumption toward CAT.
This was due to its role in generating other amino acids and as a possible energy source for metabolism.
The much greater consumption of this one amino acid was made possible by its much larger initial condition, as it was present in the cell media in the form of magnesium glutamate, ammonium glutamate, and potassium glutamate [CITE? THESIS NOT CURRENTLY IN BIBLIOGRAPHY].
Glucose made the next largest contribution, between 20\% and 30\%, dwarfing all amino acids other than glutamate.
This makes sense, as glucose powers the entire metabolism during the first hour, including energy species synthesis and amino acid synthesis.
We also investigated the energy efficiency of CAT production across the kinetic models and experimental dataset.
%The knockouts in oxidative phosphorylation also reduced the energy efficiency of CAT production  (Fig.~\ref{fig:oxphos_ko}).
The best-fit set, $\Delta$app, and experimental data had energy efficiencies of 2.6\%, $\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
The best-fit set, $\Delta$app, and experimental data had energy efficiencies of 2.6\%, calculated as a ratio of CAT production to glucose consumption, each converted into an equivalent number of ATP molecules.
$\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
%This was in line with the effect of knockouts on yield, which in turn was more or less proportional to the total amount of CAT produced in each case.
The energy efficiencies across the different cases were more or less proportional to the carbon yields, and in turn the total amount of CAT synthesis.
Taken together, these results show that oxidative phosphorylation, particularly \textit{cyd}, is important to efficient CAT production.

%Furthermore, we examined the proportion of amino acid consumption that was due to CAT synthesis in the best-fit set (Table~\ref{tbl:AA_breakdown}).
To better understand where carbon flux goes besides toward CAT, we examined the proportion of amino acid consumption that was due to CAT synthesis in the best-fit set (Table~\ref{tbl:AA_breakdown}).
Eight of the 20 amino acids had a flux-toward-CAT percentage of 100\% or higher.
For six of these (isoleucine, leucine, methionine, phenylalanine, tryptophan, valine), synthesis was inactive or negligible, meaning that CAT synthesis was the only reaction that consumed these species.
This is why methionine, and to a lesser extent isoleucine, leucine, and valine do not fit the experimental data as well as some other amino acids; consumption via CAT synthesis was not enough to fit the data, and no other reactions exist in the network to consume these species.
For histidine and tyrosine, synthesis was active, allowing the percentage to be higher than 100\%.
Another ten amino acids registered percentages lower than 100\%, meaning that they were consumed by other pathways in the network.
The most extreme of these is glutamate, with a percentage of 0.2\%, because it was consumed by numerous reactions for the synthesis of other amino acids and as an energy substrate.
Likewise, arginine, asparagine, glycine, and proline are consumed in the production of other amino acids, while cysteine and lysine are consumed to form other metabolites.
%ARG R_arg_deg1-4 go to GLU
%ASN R_asn_deg goes to ASP
%ASP R_thr, maybe negligible
%CYS cys_deg goes to pyr
%GLY R_gar goes to GLU
%LYS lys_deg goes to cadav
%PRO pro_deg goes to GLU
%SER R_glyA, maybe negligible
%THR R_thr_deg4, maybe negligible
Finally, alanine and glutamine increased during the timecourse, meaning that synthesis outweighed all consumption (including consumption toward CAT).

Sequence-specific flux balance analysis (ssFBA) predicted optimal CAT yields with no adjustable parameters (Fig.~\ref{fig:CATProdYield}).
Before exploring CFPS optimality, we first validated the ssFBA approach by comparing simulated and measured concentrations of CAT for the first hour of glucose consumption.
We chose this time window (during the first phase of CAT production) because it was approximately linear in both glucose consumption and by-/production formation.
The ssFBA calculation had no adjustable parameters; bounds on transcription and translation rates, and biochemical fluxes were either estimated from data, or
from mechanistic models parameterized from literature.
Uncertainty in experimental factors such as RNA polymerase, ribosome concentrations, elongation rates, or the upper bounds for oxygen and glucose consumption rates was addressed
by sampling plausible ranges for these parameters.
The ensemble of ssFBA simulations predicted CAT formation as a function of time during the first hour of production when constrained by the experimental metabolite data (Fig.~\ref{fig:CATProdYield}A).
Thus, the molecular description of transcription and translation were consistent with experimental measurements.
Next, to gauge the performance of the CFPS reaction, we next calculated the CAT carbon yield for three classes of constraints:
(i) theoretical maximum glucose, amino acid and oxygen upper bounds, and realistic transcriptional/translational constraints;
(ii) theoretical maximum glucose, amino acid and oxygen upper bounds, realistic transcriptional/translational constraints and knockouts of amino acid synthesis reactions of amino acids supplemented in the \textit{E. coli} extract preparation.  
(iii) metabolite fluxes constrained by the CAT data, and realistic transcriptional/translational constraints and knockouts of amino acid synthesis reactions of amino acids supplemented in the \textit{E. coli} extract preparation (Fig.~\ref{fig:CATProdYield}B).
The physiological theoretical maximum CAT carbon yield (case i) was 21.8\% $\pm$ 2.8\% (Fig.~\ref{fig:CATProdYield}B, left); this represents optimal network performance if glucose, oxygen and amino acids were produced or consumed at their upper bounds, with bounded transcription and translation rates (96\% without glucose contribution in the carbon yield calculation).
For case ii, the optimal CAT carbon yield decreased to 18.2\% $\pm$ 3.0\% (Fig.~\ref{fig:CATProdYield}B, middle).
Lastly, when metabolite constraints were applied with experimental measurements of measurements (case iii), the predicted carbon yield was 6.0\% $\pm$ 2.0\%
%By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield of 8.6\% $\pm$ 0.4\%, equivalent to 23\% of the theoretical maximum (i) and 35\% of the physiological case (ii).
By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield (without arginine and glutamate) of 7.9\%, equivalent to 36\% of the optimal case (i).
The experimental dataset had a CAT carbon yield of 8.2\%, similar to both the kinetic model and the experimentally constrained ssFBA calculation (case iii).
However, the energy efficiency was 18.1\% for case i and 15.5\% for case ii, while for case iii it was 3.9\%.
This dramatic decrease in efficiency when fluxes are constrained to data makes sense, as the network is forced toward a multitude of pathways that may not contribute to CAT production.
However, the case iii efficiency was still about 50\% higher than that of the dataset itself and the best-fit kinetic model (2.6\%).
This is likely because of the steady-state assumption and the ability to choose the optimum from a variety of flux distributions; meanwhile, the kinetic model diverts flux toward the accumulation of sub-optimal metabolites.
Thus, while the CFPS reaction was not optimal, the ssFBA calculations suggested that an approximately three-fold increase in carbon yield and a seven-fold increase in energy efficiency were theoretically possible.

@@

\begin{table}
\centering
    \caption{CAT carbon yield breakdown for best-fit set, knockouts, and experimental data. Carbon produced as CAT, carbon consumed as glucose and each amino acid, sum of consumed species (with and without arginine and glutamate), and yield  (with and without arginine and glutamate). Energy efficiency for best-fit set, knockouts, and experimental data.}
    \renewcommand{\arraystretch}{1.25}
    \begin{tabular}{lrrrrrr} \toprule
        Carbon Produced (mM) & Best-fit & $\Delta$cyd & $\Delta$nuo & $\Delta$app & $\Delta$cyd $\Delta$nuo $\Delta$app & Data \\ \hline
        CAT & 20.9 & 6.5 & 18.1 & 21.4 & 5.1 & 21.6 \\ \midrule
        Carbon Consumed (mM) \\ \hline
        GLC & 215.4 & 215.4 & 215.4 & 215.4 & 159.8 & 215.4 \\ \hline
        ALA & 0.0 & 0.0 & 1.7 & 0.0 & 0.0 & 0.0 \\ \hline
        ARG & 10.2 & 0.9 & 1.1 & 9.9 & 1.3 & - \\ \hline
        ASN & 6.2 & 6.3 & 6.2 & 6.2 & 6.3 & 6.3 \\ \hline
        ASP & 7.5 & 0.0 & 3.9 & 7.5 & 0.0 & 9.6 \\ \hline
        CYS & 3.0 & 2.9 & 3.0 & 3.1 & 2.9 & 3.7 \\ \hline
        GLN & 0.0 & 1.8 & 0.0 & 0.0 & 2.7 & 0.0 \\ \hline
        GLU & 492.6 & 505.1 & 528.2 & 505.6 & 501.8 & - \\ \hline
        GLY & 3.1 & 1.1 & 2.6 & 3.1 & 0.9 & 1.5 \\ \hline
        HIS & 0.2 & 0.4 & 1.1 & 0.2 & 0.3 & 0.0 \\ \hline
        ILE & 1.0 & 0.3 & 0.8 & 1.0 & 0.2 & 1.7 \\ \hline
        LEU & 1.4 & 0.4 & 1.2 & 1.4 & 0.3 & 2 \\ \hline
        LYS & 10.7 & 13.2 & 13.1 & 10.7 & 13.2 & 8.3 \\ \hline
        MET & 0.8 & 0.2 & 0.7 & 0.8 & 0.2 & 2.9 \\ \hline
        PHE & 3.2 & 1.0 & 2.8 & 3.3 & 0.8 & 1.6 \\ \hline
        PRO & 2.4 & 0.2 & 0.7 & 2.4 & 0.2 & 1.9 \\ \hline
        SER & 2.5 & 2.1 & 2.4 & 2.5 & 2.1 & 1.8 \\ \hline
        THR & 3.4 & 2.9 & 3.3 & 3.4 & 2.8 & 2.8 \\ \hline
        TRP & 1.0 & 0.3 & 0.8 & 1.0 & 0.2 & 1.2 \\ \hline
        TYR & 1.1 & 0.4 & 1.1 & 1.1 & 0.4 & 0.6 \\ \hline
        VAL & 1.4 & 0.4 & 1.2 & 1.5 & 0.4 & 2.4 \\ \midrule
        Sum & 767.1 & 755.3 & 791.3 & 780.1 & 696.8 & - \\ \hline
        Sum w/o ARG,GLU & 264.3 & 249.3 & 262.0 & 264.6 & 193.7 & 263.7 \\ \midrule
        Yield & 2.7\% & 0.9\% & 2.3\% & 2.7\% & 0.7\% & - \\ \hline
        Yield w/o ARG, GLU & 7.9\% & 2.6\% & 6.9\% & 8.1\% & 2.7\% & 8.2\% \\ \midrule
%        Energy Efficiency & 1.8\% & 0.6\% & 1.6\% & 1.8\% & 0.6\% & 1.9\% \\ \bottomrule
        Energy Efficiency & 2.6\% & 0.8\% & 2.2\% & 2.6\% & 0.8\% & 2.6\% \\ \bottomrule
%        Efficiencies based on ATP number of 17: 2.558085 & 0.788758 & 2.210560 & 2.611583 & 0.847068 & 2.644330
%(CAT[end]-CAT[1])*(2*219+438)/((glc[1]-glc[end])*17)*100
    \end{tabular}
\label{tbl:yield_breakdown}
\end{table}
